\documentclass[11pt,fullpage]{article}
%\usepackage{multicol,wrapfig,amsmath,subfigure}
\usepackage{multicol,amsmath,amssymb,algorithmic,bm}
\usepackage{graphics,graphicx}
\usepackage[right = 2.5cm, left=2.5cm, top = 2.5cm, bottom =2.5cm]{geometry}
\pagestyle{plain}
\def\urlfont{\DeclareFontFamily{OT1}{cmtt}{\hyphenchar\font='057}
              \normalfont\ttfamily \hyphenpenalty=10000}

%\input macros

\newcommand{\subheading}[1]{\noindent \textbf{#1}}
\newcommand{\grad}{\nabla}
\newcommand{\jump}[1]{[#1]}
\newcommand{\limit}[2]{\lim_{#1 \rightarrow #2}}
\newcommand{\mb}[1]{\mathbf{#1}}
\newcommand{\reals}[1]{\mathbb{R}^{#1}}


\begin{document}
\noindent
\begin{center}
{\bf .smesh File Format}
{\\ Fei Zhu \\ 06/10/2014}
\end{center}

\section{Introduction}

We introduce the file format for simulation mesh in Physika,
.smesh. ``smesh'' stands for ``simulation mesh'', it's not the
``.smesh'' format used by TetGen \cite{si2006}. The .smesh format is
heavily built on the .veg format developed by Jernej Barbi\v{c} in VegaFEM
\cite{vega}. Unlike VegaFEM, we do not include material properties in simulation
mesh files and .smesh files also support simulation mesh in 2D.

\section{.smesh File Format}

\textbf{Basics:} The smesh file format is ASCII. Lines starting with *
denote a command. Lines starting with
\# are comments. Empty lines are ignored. Files can be nested using
the *INCLUDE command. The effect of *INCLUDE is to include, at that
point in the .smesh file, the entire contents of the included
file. Include files can include other files; they can nest
arbitrarily.
\\\\
\noindent{}\textbf{Vertices:} Vertices are specified using the *VERTICES
keyword. The second line gives the number of vertices, followed by
integer ``2'' (two-dimensional simulation) or ``3'' (three-dimensional
simulation), optionally followed by more parameters, which are
ignored. The subsequent lines give one vertex per line, in the format:
\\\\
\noindent{}$<$vertex index$>$ $<$x$>$ $<$y$>$ [z]
\\\\
\noindent{}where the vertex index starts either at 0 or 1, increments by 1 for
every vertex. The unit for vertex positions is meters.
\\\\
\noindent{}2D example:
\\\\
\noindent{}*VERTICES\\
5 2 0 0\\
1 0.5 0.5\\
2 1.0 -0.5\\
3 -1.0 0.0\\
4 0.25 -0.25\\
5 0.6 0.2\\

\noindent{}3D example:
\\\\
\noindent{}*VERTICES\\
5 3 0 0\\
1 0.5 0.5 0.5\\
2 1.0 -0.5 0.5\\
3 -1.0 0.0 1.0\\
4 0.25 -0.25 0.5\\
5 0.6 0.2 0.3
\\\\
\noindent{}\textbf{Elements:} Elements are specified using the
*ELEMENTS keyword. The second line gives the element type, namely
``TRI'', ``QUAD'', ``TET'' or ``CUBIC''. ``TET'' and ``CUBIC'' stand
for tetrahedral and cubic mesh for 3D simulation, ``TRI'' and ``QUAD''
are their counterparts in 2D. The third line gives the
number of mesh elements, followed by the number of vertices in each
element (3 for triangles, 4 for quads and tets, 8 for cubes), followed
by some optional integers that are ignored. Subsequent lines give one
element per line, in the format:
\\\\
\noindent{}$<$element index$>$ $<$vertex 1$>$ $\cdots$ $<$vertex n$>$
\\\\
\noindent{}where the element index starts either at 0 or 1 and
increments by 1 for every element. Example:
\\\\
\noindent{}*ELEMENTS\\
TETS\\
2 4 0\\
1 2 3 4 1\\
2 5 3 4 1
\\\\
\noindent{} specifies a mesh with two tets. The first tet has vertices
2, 3, 4, 1 (in that order), and the second tet has vertices 5, 3, 4,
1. The ordering of vertices within the element matters. Incorrect
order give wrong results.
\\\\
\noindent{}\textbf{Sets:} Sets store a set of integer indices. They
are used to store indices of elements that share the same property,
for example material property. Sets are specified using the *SET
keyword, followed by the name of the set. The next lines are
comma-separated list of set elements. Elements should be stored and
identified by the indices given in the *ELEMENTS section, i.e., either
0-indexed or 1-indexed, depending on whether *ELEMENTS are given
0-indexed or 1-indexed. Example:
\\\\
\noindent{}*SET set1\\
\noindent{}11,17,21,37,113,310,555,\\
\noindent{}556,557,570,601,991,1013,1210,1225
\\\\
\noindent{}\textbf{Easy re-use of Stellar/TetGen meshes:} The .smesh file format supports
easy re-use of Stellar/TetGen meshes since it's derived from .veg
file. Suppose that the mesh vertices and elements are stored in
myMesh.node and myMesh.ele files, in the standard Stellar/TetGen
format. The following ``template'' .smesh file is the shortest way to
import those meshes into a .smesh file:
\\\\
\noindent{}*VERTICES\\
*INCLUDE myMesh.node\\
*ELEMENTS\\
TETS\\
*INCLUDE myMesh.ele

\bibliographystyle{eg-alpha}
\bibliography{ref}

\end{document}